Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-16 R0V0.tex
Modify the paragraph about the ADMM (reverted from commit 1a3a8b77133ebd4ba55143aedd828da5421ce7e1)

\mypara In the remaining of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b

@@

\mypara Note that the ADMM cannot be employed to compute $W$ using the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, in this case. This follows from the fact that $\ker(B)\equiv0$.

>>>>

\mypara In the remained of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b

@@

\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual},  the solver took 23 seconds to compute the matrix $W$ for system~\eqref{eq:example} with four agents lead to the
